Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-20 ba_resubmit/kundinger_resubmit2.tex
making more comments.
working on revisions.

Next, the full conditional for $\pi$ is given by
\begin{align}
	\pi^{(s+1)}|\bm{Z}^{(s)},  \alpha_{\pi}, \beta_{\pi}, \pi \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

@@

\begin{enumerate}	
\item \textcolor{red}{Note that 	$\gamma_{Z_j, j}$ doesn't appear to be defined.}
\item \textcolor{red}{There appears to be no update for $\pi$ in this section.}
\item Make sure when you give the update for the new efficient full conditional, you give the s, s+1. Example, it's missing on the update for $m$ and $u$ so it's not immediately clear how one would draw this directly. Wouldn't it just be a vectorized Dirichlet, where the computational savings come from vectorizing the hyperparameters of the Dirichlet?
\end{enumerate}

@@

\textcolor{red}{Some statement regarding $\pi$ needs to go here even if it's that you draw from the same distribution as in the original sampler.}

@@

	\hypertarget{app:derivations}{%
	\section{Derivations of Full Conditionals}\label{app:derivations}}
\textcolor{red}{Note: Please use s, s+1 consistently throughout. Or supress the notation and tell the reader. It looks weird to go back and forth. I've tried to provide an intermediate solution. Perhaps Jerry can state if he would think this is okay as an Editor.}\\

>>>>

Next, the full conditional for $\pi$ is given by
\begin{align}
\label{eqn:pi}
	\pi^{(s+1)}|\bm{Z}^{(s)},  \alpha_{\pi}, \beta_{\pi}, \pi \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

@@

\begin{enumerate}	
\item \textcolor{red}{Note that 	$\gamma_{Z_j, j}$ doesn't appear to be defined. Also, do you more formally mean something like as follows: Consider $\gamma_{q,q} = h_p \mid Z_j = q$. It seems that the conditioning may actually be important here. I mention this for two reasons, it appears a bit strange in equation (22). When I think through it, it's okay. I just wanted to bring it up as a conversation before submission.}
\item \textcolor{red}{There appears to be no update for $\pi$ in this section, so I have added one in.}
\item Make sure when you give the update for the new efficient full conditional, you give the s, s+1. Example, it's missing on the update for $m$ and $u$ so it's not immediately clear how one would draw this directly. Wouldn't it just be a vectorized Dirichlet, where the computational savings come from vectorizing the hyperparameters of the Dirichlet?
\end{enumerate}

@@

\textcolor{teal}{Turning to sampling for $\pi,$ it remains the same as in (\ref{eqn:pi}). }

@@

	\hypertarget{app:derivations}{%
	\section{Derivations of Full Conditionals}\label{app:derivations}}
\textcolor{red}{Note: Please use s, s+1 consistently throughout. Or surpress the notation and tell the reader. It looks weird to go back and forth. I've tried to provide an intermediate solution. Perhaps Jerry can state if he would think this is okay as an Editor.}\\
